### 2025-09-03 download-football-data.qmd
20250902 - historical actual team stats

>>>>

### Historical Actual Team Statistics {#sec-downloadActualTeamStats}

@HoTeamStats provide a Data Dictionary for historical actual team statistics data at the following link: <https://nflreadr.nflverse.com/articles/dictionary_team_stats.html>.
You can also access the data dictionary via `R` using the following syntax:

nflreadr::dictionary_team_stats
```

nfl_actualStats_team_weekly_raw <- progressr::with_progress(
  nflreadr::load_team_stats(
    seasons = TRUE,
    summary_level = "week"))

nfl_actualStats_team_seasonal_reg_raw <- progressr::with_progress(
  nflreadr::load_team_stats(
    seasons = TRUE,
    summary_level = "reg"))

nfl_actualStats_team_seasonal_regPost_raw <- progressr::with_progress(
  nflreadr::load_team_stats(
    seasons = TRUE,
    summary_level = "reg+post"))
```

save(
  nfl_actualStats_team_weekly_raw,
  nfl_actualStats_team_seasonal_reg_raw,
  nfl_actualStats_team_seasonal_regPost_raw,
  file = "./data/nfl_actualStats_team_raw.RData"
)
```

load(file = "./data/nfl_actualStats_team_raw.RData")
```

The `nfl_actualStats_team_weekly_raw` object is in `season`-`week`-`team` form.
That is, each row should be uniquely identified by the combination of `season`, `week`, and `team`.
Let's rearrange the data accordingly:

```{r}
nfl_actualStats_team_weekly <- nfl_actualStats_team_weekly_raw %>% 
  select(season, week, team, everything()) %>% 
  arrange(season, week, team)
```

Let's check for duplicate `season`-`week`-`team` instances:

```{r}
nfl_actualStats_team_weekly %>% 
  group_by(season, week, team) %>% 
  filter(n() > 1) %>% 
  head()
```

```{r}
names(nfl_actualStats_team_weekly) %>% as.data.frame()
```

The `nfl_actualStats_team_seasonal_reg_raw` and `nfl_actualStats_team_seasonal_regPost_raw` objects are in `season`-`team` form.
That is, each row should be uniquely identified by the combination of `season` and `team`.
Let's rearrange the data accordingly:

```{r}
nfl_actualStats_team_seasonal_reg <- nfl_actualStats_team_seasonal_reg_raw %>% 
  select(season, team, everything()) %>% 
  arrange(season, team)

nfl_actualStats_team_seasonal_regPost <- nfl_actualStats_team_seasonal_regPost_raw %>% 
  select(season, team, everything()) %>% 
  arrange(season, team)
```

Let's check for duplicate `season`-`week`-`team` instances:

```{r}
nfl_actualStats_team_seasonal_reg %>% 
  group_by(season, team) %>% 
  filter(n() > 1) %>% 
  head()

nfl_actualStats_team_seasonal_regPost %>% 
  group_by(season, team) %>% 
  filter(n() > 1) %>% 
  head()
```

save(
  nfl_actualStats_team_weekly,
  nfl_actualStats_team_seasonal_reg,
  nfl_actualStats_team_seasonal_regPost,
  file = "./data/nfl_actualStats_team.RData"
)
```

load(file = "./data/nfl_actualStats_team.RData")
```
